Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Guideline for International \emph{and Domestic} Students

### 2024-02-10 demystify.tex

Most PhD programs will require at least \textbf{two LORs}. Having a letter from an internationally recognized researcher can \textbf{greatly} strengthen your application. In fact, it is arguable at many top CS programs, strong LoRs from well-known researchers are even more important than published papers.

>>>>

Most PhD programs will require at least \textbf{two LORs}. Having a letter from an internationally recognized researcher will greatly strengthen your application. In fact, a strong letter from a well-known researcher can outweigh the lack of publications.
